### 2023-01-03 paper.Rmd
editing

    Anticlustering refers to the process of partitioning elements into disjoint groups with the goal of obtaining high between-group similarity and high within-group heterogeneity. Anticlustering thereby reverses the logic of its better known twin---cluster analysis---and is usually approached by maximzing instead of minimizing a clustering objective function. Introducing k-plus, this paper presents an extension of the k-means clustering objective to maximize between-group similarity in anticlustering applications. The k-plus criterion represents between-group similarity as discrepancy in distribution moments (means, variance, higher order moments, and covariances), while the classical k-means criterion only reflects the degree to which groups differ in their means. It is shown that the k-plus criterion can be reduced to an augmentation of the input data while the original k-means objective remains unchanged. A computer simulation and practical examples show that k-plus anticlustering achieves high between-group similarity with regard to multiple objectives. In particular, optimizing between-group similarity with regard to variances as well as means comes with almost no cost to either criterion; the k-plus extension is therefore generally preferred over classical k-means anticlustering. Higher order moments and covariance structure can also succesfully be equalized. Example are given on how k-plus anticlustering can be applied to real norming data using the open source R package `anticlust`, which is freely available via CRAN (https://cran.r-project.org/package=anticlust) and Github (https://github.com/m-Py/anticlust).

@@

Oftentimes, partitioning applications in psychology are focused on between-group similarity rather than within-group heterogeneity (even though both goals oftentimes coincide). High between-group similarity is for example desirable when preparing experimental conditions that use different stimulus sets, that should however be as similar as possible with regard to response-relevant attributes [@lahl2006]. Rather than relying on pairwise (dis)similarity ratings, stimulus selection tasks are usually conducted on the basis of attribute data. That is, individual stimuli are numerically coded on relevant dimensions [@dry2009]. For stimuli in psycholinguistic experiments, attributes may consist of ratings for imagery and concreteness, as well as orthographic variables [@friendly1982]. In other cases, attributes are binary and may represent the presence or absence of a feature [@tversky1977]. In the context of anticlustering, one approach for handling attribute data is to compute an appropriate dissimilarity measure such as the pairwise Euclidean or squared Euclidean distance across the set of attributes [@brusco2019]. Subsequently, a distance-based anticlustering criterion such as the diversity can be optimized to obtain a partitioning of the stimuli. A different anticlusting approach relies on clustering objectives that can directly be computed on the attribute values. K-means is probably the best-known objective of this kind. In k-means clustering, the sum of the squared Euclidean distances between data points and their cluster centers is minimized, usually using the k-means heuristic [@jain2010; @steinley2006; @brusco2006branch]. Minimizing the k-means criterion simultaneously maximizes between-cluster separation and within-cluster homogeneity [@aloise2009np]. Reversing the k-means objective function---using maximization instead of minimization---has been recognized as a useful approach when aiming for high between-group similarity [@spath1986; @valev1998; @valev1983]. Specifically, as @spath1986 noted, k-means anticlustering minimizes differences with regard to the means of the numeric attributes across clusters. However, other distribution characteristics---such as the variance---are not targeted. @papenberg2020 showed that k-means anticlustering tends to over-optimize between-group similarity with regard to the mean at the cost of similarity in spread; even an entirely random group assignment usually resulted in more similar variances. When requiring overall between-group similarity, the negligence of distribution characteristics other than the mean is misguided, because similar means can be obtained even when the underlying distributions are clearly different [e.g., @anscombe1973].

To optimize overall between-group similarity---and hence to overcome the limitations of k-means anticlustering---this paper introduces k-plus anticlustering. K-plus is an extension of the k-means objective that quantifies between-group similarity as discrepancy with regard to several distribution characteristics instead of only the mean. Specifically, k-plus offers the possibility to minimize differences with regard to the variance, covariances, and higher order moments such as skewness and kurtosis. After formally introducing the k-plus objective, a simulation study is reported showing that k-plus anticlustering is well suited to create groups having minimal differences according to multiple distribution characteristics. Practical examples illustrate how readers can easily apply k-plus anticlustering using the free and open source software package `anticlust`, an extension to the popular statistical programming language R [@papenberg2020; @R-base; @R-anticlust].

@@

For the purpose of problem formalization, I adopt the notation @steinley2006 provided in his comprehensive synthesis of half a century of research on k-means. K-means anticlustering is used to partition $N$ elements each having $P$ attributes into $K$ groups $(C_1, \ldots, C_K)$, where $C_k$ is the set of $n_k$ objects in the $k$'th group. The partitioning is subject to the requirement that each element is assigned to exactly one group. In anticlustering applications, an additional constraint is usually imposed on the group sizes $n_k$, where the most common restriction requires that all groups have equal size [@papenberg2020].

@@

In the following, I present a variation of the $\mathit{SSE}$ that quantifies how the variance of numeric data differs between groups. To motivate the new criterion, we first consider a set of one-dimensional observations. The sample variance of a set of observations $x = (x_1, \ldots, x_N)$ is computed as the mean of the squared distances between observations and their mean $\overline{\mathbf{x}}$:

@@

This formula again has the same form as $\mathit{SSE}$ (and $\mathit{SSE_{Var}}$), but is computed on different data. In this case, both the original data $x_{ij}$ as well as the squared distances $y_{ij}$ are used as attributes that enter the objective function. That is, computing the k-plus criterion can be done by first computing the values $y_{ij}$, appending these to the original data matrix, and then computing the $\mathit{SSE}$ on the augmented data matrix. Hence, using the unweighted sum approach, k-plus anticlustering reduces to an augmentation of the data matrix, leaving the original k-means criterion unchanged.

Note that a problem may arise if the weights $w_1$ and $w_2$ are ignored when optimizing the k-plus objective, i.e., when just appending the squared-distance-features to the data set. Since the computation of the data matrix $\mathbf{Y}_{N \times P}$ involves squaring, the squared distances $y_{ij}$ usually have much larger values, on average, than the raw values $x_{ij}$. Therefore, the $\mathit{SSE_{Var}}$ criterion naturally receives greater weight when computing $\mathit{SSE_{kplus}}$ than the standard $\mathit{SSE}$ criterion. This imbalance is most likely unwarranted because optimizing similarity with regard to variances is not more important than optimizing similarity with regard to means. A solution is to standardize all values $x_{ij}$ and $y_{ij}$ to the same scale before computing $SSE_{kplus}$, e.g. via $z$-standardization.

@@

When optimizing a bicriterion objective such as $\mathit{SSE_{kplus}}$, the ideal outcome would be to find a partition where both the means and the variances are very similar between groups. However, research on multi-objective optimization has shown that cases are rare where a single solution satisfies all criteria to an optimal degree, making a tradeoff necessary [@ferligoj1992direct]. A motivating example illustrates that in the case of anticlustering, aiming to simultaneously optimize similarity of means and variances may however be feasible. I created 14 data points following a univariate normal distribution ($M = 15$, $SD = 3$) and then generated all `r n_partitions(14, 2)` possible ways to partition the 14 data points into $K = 2$ equal-sized groups. Figure 1 shows the scatterplot of the criteria $\mathit{SSE}$ and $\mathit{SSE_{Var}}$ across partitions. To divide the 14 elements into two groups that are similar with regard to their mean and variance, a partition should be chosen that is depicted in the upper right corner of the scatterplot. The partition that is represented by the squared symbol has the overall best highest $\mathit{SSE}$, but is outperformed by many other partitions with regard to $\mathit{SSE_{Var}}$. Similarly, the partition that maximizes $\mathit{SSE_{Var}}$ (the triangular symbol in Figure 1) is not well-suited to optimize $\mathit{SSE}$ at the same time. The diamond symbol represents the partition that maximizes $\mathit{SSE_{kplus}}$, i.e., the sum of $\mathit{SSE}$ and $\mathit{SSE_{Var}}$. This partition is located in the right upper corner and yields `r df$kmeans[which.max(df$kplus)] / max(df$kmeans) * 100`% of the global maximum $\mathit{SSE}$, and `r df$kvar[which.max(df$kplus)] / max(df$kvar) * 100`% of the global maximum value of $\mathit{SSE_{Var}}$. Thus, the optimal partition according to $\mathit{SSE_{kplus}}$ fulfills the two constituting criteria $\mathit{SSE}$ and $\mathit{SSE_{Var}}$ to an astonishing degree.

@@

The k-plus approach to equalizing the variance between groups can be generalized to higher order moments in a straight forward manner. The *j*'th sample moment of a variable $x = (x_1, \ldots, x_N)$ can be computed as

@@

Because the covariance is also defined as an expected value, the k-plus criterion can be extended to reflect differences in covariances between data sets. The covariance between two variables $x$ and $y$ is defined as

@@

Thus, to maximize between-group similarity with regard to covariance structure, it is possible to add an additional variable for each pair of variables $x$ and $y$, computed as $(x_i - \overline{\mathbf{x}}) (y_i -\overline{\mathbf{y}})$. This requires computing $\binom{N}{2}$ new variables and thus turns out be be rather costly: The number of additional variables needed to minimize differences with regard to covariance structure grows quadratically with increasing number of variables; the number of additional variables needed to minimize differences with regard to distribution moments only grows linearly with increasing number of variables.

@@

To thoroughly evaluate the k-plus approach to anticlustering, three specific k-plus criteria were implemented in a simulation study: (i) "standard" k-plus anticlustering, minimizing differences with regard to the mean and variance; (ii) k-plus *skew/kurtosis*, minimizing differences with regard to the mean, variance, skew and kurtosis; (iii) k-plus *correlation*, minimizing differences with regard to the mean, variance and covariance structure. To implement all k-plus objectives, the simple unweighted sum outlined above approach was employed. Thus, when optimizing a k-plus criterion, the original data matrix was extended to incorporate the additional criteria. Subsequently, the original k-means criterion $\mathit{SSE}$ was maximized on the basis of the augmented data set.

@@

The same local maximum search [Method LCW, @weitz1998] was applied to optimize each of the five competing anticlustering objectives. Building on an initial random assignment of elements to groups, the algorithm proceeds by swapping elements between groups in such a way that each swap improves the objective criterion by the largest possible margin. That is, for each element, all possible exchanges with elements in other clusters are simulated and the resulting objective values are stored. After each exchange has been evaluated, the one exchange is realized that improves the objective the most. No exchange is realized if no improvement is possible. The exchange procedure is repeated for each element. Once the last element has been processed, the procedure restarts at the beginning and once again iterates through all elements, repeating the exchange procedure. The procedure stops as soon as an iteration through the entire data set no longer yielded an improvement, i.e., as soon as a local maximum has been found. To obtain better results, this local maximum search may be initialized multiple times [@spath1986]. The simulation study always employed five repetitions of the local maximum search.

@@

foo <- apa_table(
  tab,
  caption = "Results of the simulation study",
  note = "The global results of the simulation study aggregated across all conditions. Cells contain information about the average between-group discrepancy with regard to means, standard deviations, skewness, kurtosis, and correlations. Lower values indicate less discrepancy, i.e., higher between-group similarity. Each cell value is the result of averaging across 30,000 data points (10,000 data sets $\\times$ $K = 2$, $K = 3$ or $K = 4$).",
  escape = FALSE,
  align = c("r")
)

@@

Figure 2 shows that with increasing $N$, k-means and the k-plus methods converged on the same level with regard to minimizing $\Delta \mathit{M}$. This is an important observation because it shows that including the k-plus term in the optimization process does not necessarily prevent minimizing discrepancy in means; instead, multiple objectives can be addressed at the same time---especially when $N$ increases. However, while k-plus anticlustering is capable of addressing multiple objectives simultaneously, increasing the number of optimization criteria apparently aggravates fulfilling each single criterion. Hence, k-plus skew/kurtosis and k-plus correlation performed worse at minimizing $\Delta \mathit{SD}$ than standard k-plus. Still, every k-plus method did what it was supposed to do: k-plus skew/kurtosis was best at minimizing $\Delta \mathit{Skew}$ and $\Delta \mathit{Kurtosis}$, k-plus correlation was best at minimizing discrepancy with regard to $\Delta \mathit{Cor}$. At the same time, these two k-plus objectives maintained a comparably good level of addressing $\Delta \mathit{M}$ and $\Delta \mathit{SD}$, outperforming diversity anticlustering.

It is maybe surprising that k-plus skew/kurtosis does not seem to have performed much better than diversity anticlustering with regard to skewness and---in particular---kurtosis, even though the method has been specifically tailored to these criteria. Figure 2 gives a more fine grained assessment of this observation by splitting the results by $N$: Surprisingly, for small $N$, k-plus skew/kurtosis was even worse than diversity anticlustering at minimizing $\Delta \mathit{Skew}$ and $\Delta \mathit{Kurtosis}$. However, with increasing $N$, it clearly outperformed diversity anticlustering. These results illustrate the cost of optimizing several criteria at the same time: for low $N$, k-plus seems skew/kurtosis to be preoccupied with fulfilling the objectives $\Delta \mathit{M}$ and $\Delta \mathit{SD}$. Increasing $N$ then facilitated to also address $\Delta \mathit{Skew}$ and $\Delta \mathit{Kurtosis}$.

>>>>

    Anticlustering refers to the process of partitioning elements into disjoint groups with the goal of obtaining high between-group similarity and high within-group heterogeneity. Anticlustering thereby reverses the logic of its better known twin---cluster analysis---and is usually approached by maximzing instead of minimizing a clustering objective function. Introducing k-plus, this paper presents an extension of the k-means clustering objective to maximize between-group similarity in anticlustering applications. The k-plus criterion represents between-group similarity as discrepancy in distribution moments (means, variance, higher order moments, and covariances), while the classical k-means criterion only reflects the degree to which groups differ in their means. It is shown that the k-plus criterion can be reduced to an augmentation of the input data while the original k-means objective remains unchanged. A computer simulation and practical examples show that k-plus anticlustering achieves high between-group similarity with regard to multiple objectives. In particular, optimizing between-group similarity with regard to variances usually does not compromise similarity with regard to means; the k-plus extension is therefore generally preferred over classical k-means anticlustering. Example are given on how k-plus anticlustering can be applied to real norming data using the open source R package `anticlust`, which is freely available via CRAN (https://cran.r-project.org/package=anticlust) and Github (https://github.com/m-Py/anticlust).

@@

Oftentimes, partitioning applications in psychology are focused on between-group similarity rather than within-group heterogeneity, even though both goals oftentimes coincide. High between-group similarity is for example desirable when designing experimental conditions using different stimulus sets that should be as similar as possible with regard to response-relevant attributes [@lahl2006]. Stimulus selection tasks are usually conducted on the basis of attribute data and not on pairwise (dis)similarity ratings. That is, individual stimuli are numerically coded on relevant dimensions [@dry2009]. For stimuli in psycholinguistic experiments, attributes may consist of ratings for imagery and concreteness, as well as orthographic variables [@friendly1982]. In other cases, attributes are binary and may represent the presence or absence of a feature [@tversky1977]. In the context of anticlustering, one approach for handling attribute data is to compute an appropriate dissimilarity measure such as the pairwise Euclidean or squared Euclidean distance across the set of attributes [@brusco2019]. Subsequently, a distance-based anticlustering criterion such as the diversity can be optimized to obtain a partitioning of the stimuli. A different anticlusting approach relies on clustering objectives that can directly be computed on the attribute values. K-means is probably the best-known objective of this kind. In k-means clustering, the sum of the squared Euclidean distances between data points and their cluster centers is minimized, usually using the k-means heuristic [@jain2010; @steinley2006; @brusco2006branch]. Minimizing the k-means criterion simultaneously maximizes between-cluster separation and within-cluster homogeneity [@aloise2009np]. Reversing the k-means objective function---using maximization instead of minimization---has been recognized as a useful approach when aiming for high between-group similarity [@spath1986; @valev1998; @valev1983]. Specifically, as @spath1986 noted, k-means anticlustering minimizes differences with regard to the means of the numeric attributes across clusters. However, other distribution characteristics---such as the variance---are not targeted. @papenberg2020 showed that k-means anticlustering tends to over-optimize between-group similarity with regard to the mean at the cost of similarity in variance. However, when aiming for overall between-group similarity, the negligence of distribution characteristics other than the mean is misguided; similar means can be obtained even when the underlying distributions are clearly different [e.g., @anscombe1973].

To optimize overall between-group similarity---and hence to overcome the limitations of k-means anticlustering---this paper introduces k-plus anticlustering. K-plus is an extension of the k-means objective that quantifies between-group similarity as discrepancy with regard to several distribution characteristics instead of only the mean. Specifically, k-plus offers the possibility to minimize differences with regard to the variance, covariances, and higher order moments such as skewness and kurtosis. After formally introducing the k-plus objective, a simulation study shows that k-plus anticlustering is well suited to create groups having minimal differences according to multiple distribution characteristics. Practical examples illustrate how readers can easily apply k-plus anticlustering using the free and open source software package `anticlust`, an extension to the popular statistical programming language R [@papenberg2020; @R-base; @R-anticlust].

@@

For the purpose of problem formalization, I adopt the notation @steinley2006 provided in his comprehensive synthesis of half a century of research on k-means. K-means anticlustering is used to partition $N$ elements each having $P$ attributes into $K$ groups $(C_1, \ldots, C_K)$. The partitioning is subject to the requirement that each element is assigned to exactly one group. In anticlustering applications, an additional constraint is usually imposed on the group sizes, with the most common restriction being that all groups have equal size [@papenberg2020].

@@

In the following, I present a variation of the $\mathit{SSE}$ that quantifies how the variance of numeric data differs between groups. To motivate the new criterion, we first consider a set of one-dimensional observations. The sample variance of a set of $N$ observations $x = (x_1, \ldots, x_N)$ is computed as the mean of the squared distances between observations and their mean $\overline{\mathbf{x}}$:

@@

This formula again has the same form as $\mathit{SSE}$ but is computed on different data. In this case, both the original data $x_{ij}$ as well as the squared distances $y_{ij}$ are used as attributes that enter the objective function. That is, computing the k-plus criterion can be done by first computing the values $y_{ij}$, appending these to the original data matrix, and then computing the $\mathit{SSE}$ on the augmented data matrix. Hence, using the unweighted sum approach, k-plus anticlustering reduces to an augmentation of the data matrix, leaving the original k-means criterion unchanged. Note that a problem may arise if the weights $w_1$ and $w_2$ are ignored when optimizing the k-plus objective. Since the computation of the $y_{ij}$ involves squaring, their range of values is expected to be very different from the raw values $x_{ij}$. This imbalance can strongly and unpredictably influence the relative weight of $\mathit{SSE}$ and $\mathit{SSE_{Var}}$ when computing $\mathit{SSE_{kplus}}$. A solution is to standardize all values $x_{ij}$ and $y_{ij}$ to the same scale before computing $\mathit{SSE_{kplus}}$, e.g. via $z$-standardization.

@@

When optimizing a bicriterion objective such as $\mathit{SSE_{kplus}}$, the ideal outcome would be to find a partitioning where both constituting criteria (mean and variance) are similar between groups. Although research on multi-objective optimization has shown that solutions oftentimes fail to simultaneously satisfy several criteria [@ferligoj1992direct], a motivating example illustrates that in the case of anticlustering, aiming to simultaneously optimize similarity of means and variances may be feasible. I created 14 data points following a univariate normal distribution ($M = 15$, $SD = 3$) and then generated all `r n_partitions(14, 2)` possible ways to partition the 14 data points into $K = 2$ equal-sized groups. Figure 1 shows the scatterplot of the criteria $\mathit{SSE}$ and $\mathit{SSE_{Var}}$ across partitions. The partition that is represented by the squared symbol has the overall best highest $\mathit{SSE}$, but is outperformed by many other partitions with regard to $\mathit{SSE_{Var}}$. Similarly, the partition that maximizes $\mathit{SSE_{Var}}$ (the triangular symbol in Figure 1) is not well-suited to optimize $\mathit{SSE}$ at the same time. Thus, when only considering one of the objectives, the mathematically optimal partitioning fails to establish groups that are similar both with regard to their means and variances. The diamond symbol represents the partition that maximizes $\mathit{SSE_{kplus}}$, which yields `r df$kmeans[which.max(df$kplus)] / max(df$kmeans) * 100`% of the global maximum $\mathit{SSE}$, and `r df$kvar[which.max(df$kplus)] / max(df$kvar) * 100`% of the global maximum value of $\mathit{SSE_{Var}}$. Thus, the optimal partition according to $\mathit{SSE_{kplus}}$ fulfills the two constituting criteria $\mathit{SSE}$ and $\mathit{SSE_{Var}}$ to an astonishing degree.

@@

The k-plus approach to equalizing the variance can be generalized to higher order moments. The *j*'th sample moment of a variable $x = (x_1, \ldots, x_N)$ can be computed as

@@

Because the covariance is also defined as an expected value, the k-plus logic can be extended to minimize differences with regard to covariance structure. The covariance between two variables $x = (x_1, \ldots, x_N)$ and $y = (y_1, \ldots, y_N)$ is defined as

@@

Thus, to maximize between-group similarity with regard to covariance structure, it is possible to augment the data set with an additional variable for each pair of variables $x$ and $y$, computed as $(x_i - \overline{\mathbf{x}}) (y_i -\overline{\mathbf{y}})$.

@@

To thoroughly evaluate the k-plus approach to anticlustering, three specific k-plus criteria were implemented in a simulation study: (i) "standard" k-plus anticlustering, minimizing differences with regard to the mean and variance; (ii) k-plus *skew/kurtosis*, minimizing differences with regard to the mean, variance, skew and kurtosis; (iii) k-plus *correlation*, minimizing differences with regard to the mean, variance and covariance structure. To implement all k-plus objectives, the unweighted sum approach was employed. Thus, to optimize a k-plus criterion, the original data set was augmented to incorporate the additional criteria; subsequently, the original k-means criterion $\mathit{SSE}$ was maximized on the basis of the augmented data set.

@@

The same local maximum search [Method LCW, @weitz1998] was applied to optimize each of the five competing anticlustering objectives. Building on an initial random assignment, the algorithm proceeds by swapping elements between groups in such a way that each swap improves the objective criterion by the largest possible margin. That is, it starts with the first element and simulates all exchanges with elements that are currently assigned to a different group. After each exchange has been processed, the one exchange is realized that improves the objective function the most. No exchange is realized if no improvement is possible. The exchange process is repeated for each element. After that, the procedure restarts at the beginning and is repeated until an iteration through the entire data set no longer yields an improvement. To obtain better results, this local maximum search may be initialized multiple times [@spath1986]. The simulation study always employed five repetitions of the local maximum search.

@@

apa_table(
  tab,
  caption = "Results of the simulation study",
  note = "The global results of the simulation study aggregated across all conditions. Cells contain information about the average between-group discrepancy with regard to means, standard deviations, skewness, kurtosis, and correlations. Lower values indicate less discrepancy, i.e., higher between-group similarity. Each cell value is the result of averaging across 30,000 data points (10,000 data sets $\\times$ $K = 2$, $K = 3$ or $K = 4$).",
  escape = FALSE,
  align = c("r")
)

@@

Figure 2 shows that with increasing $N$, k-means and the k-plus methods converged on the same level with regard to minimizing $\Delta \mathit{M}$. This is an important observation because it shows that including the k-plus term in the optimization process does not necessarily prevent minimizing discrepancy in means; instead, multiple objectives can be addressed at the same time---especially when $N$ increases. However, while k-plus anticlustering was capable of addressing multiple objectives simultaneously, increasing the number of optimization criteria aggravated fulfilling each single criterion: k-plus skew/kurtosis and k-plus correlation performed worse at minimizing $\Delta \mathit{M}$ and $\Delta \mathit{SD}$ than standard k-plus. However, every k-plus method did what it was supposed to do: k-plus skew/kurtosis was best at minimizing $\Delta \mathit{Skew}$ and $\Delta \mathit{Kurtosis}$, k-plus correlation was best at minimizing discrepancy with regard to $\Delta \mathit{Cor}$. At the same time, these two k-plus objectives maintained a comparably good level of addressing $\Delta \mathit{M}$ and $\Delta \mathit{SD}$, outperforming diversity anticlustering.

It is maybe surprising that k-plus skew/kurtosis does not seem to have performed much better than diversity anticlustering with regard to skewness and---in particular---kurtosis, even though the method has been specifically tailored to these criteria. Figure 2 gives a more fine grained assessment of this observation by splitting the results by $N$: Surprisingly, for small $N$, k-plus skew/kurtosis was even worse than diversity anticlustering at minimizing $\Delta \mathit{Skew}$ and $\Delta \mathit{Kurtosis}$. However, with increasing $N$, it clearly outperformed diversity anticlustering. These results illustrate the cost of optimizing several criteria at the same time: for low $N$, k-plus skew/kurtosis was apparently preoccupied with fulfilling the objectives $\Delta \mathit{M}$ and $\Delta \mathit{SD}$. Increasing $N$ then facilitated to also address $\Delta \mathit{Skew}$ and $\Delta \mathit{Kurtosis}$.
